### 2014-08-17 paper/GAME_HARD_01_INTRODUCTION.tex
Implemented build script in Perl rather than Python because of downtime.

% INTRODUCTION
\section{INTRODUCTION}
\label{sec:introduction}
When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, or memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU performance).
The increased utilization of complex GPU-kernels has brought forth the need of more extensive debugging- and profiling-options involving access of data that may be difficult to retrieve from hardware.
Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU (General-Purpose computing on Graphics Processing Units) technologies, possibly due to architectural differences between chip manufacturers.
A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework~\citeweb[]{gpuocelot}, often in exchange for substantial performance implications.
Other resons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwise unavailable~\citeweb[]{warp}.

>>>>

% INTRODUCTION
\section{INTRODUCTION}
\label{sec:introduction}
When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, or memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU performance).
The increased utilization of complex GPU-kernels has brought forth the need of more extensive debugging- and profiling-options involving access of data that may be difficult to retrieve from hardware.
Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU (General-Purpose computing on Graphics Processing Units) technologies, possibly due to architectural differences between chip manufacturers.
A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework~\citeweb[]{gpuocelot}, often in exchange for substantial performance implications.
Other reasons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existent, when hardware is busy, or otherwise unavailable~\citeweb[]{warp}.
